### 2018-04-27 paper/building-blocks.tex

\subsection{\Aclp*{KEM}}\label{KEM}

@@

\begin{figure}
  \begin{algorithmic}
    \Require{$\Enc$ is an IND-CCA encryption scheme, $\Sign$ is a one-time 
      signature scheme.}

@@

\begin{frame}
  \begin{figure}
    \begin{algorithmic}
      \Require{$\Enc$ is an IND-CCA encryption scheme, $\Sign$ is a one-time 
        signature scheme.}

>>>>

\subsection{Hybrid encryption}\label{KEM}

\Iac{HE} scheme is a combination of \iac{PKE} scheme and \iac{SKE} scheme.
The \ac{PKE} scheme is used as \iac{KEM} to encrypt a symmetric key for the 
\ac{SKE} scheme.
Then the \ac{SKE} scheme is used as \iac{DEM} to encrypt the actual data.

Whenever we use \iac{PKE} scheme, we mean to employ it in \iac{HE} scheme.

@@

\begin{figure}
  \begin{algorithmic}
    \Require{$\Enc$ is an IND-CCA \ac{PKE} scheme, $\Sign$ is a one-time 
      signature scheme.}

@@

\begin{frame}
  \begin{figure}
    \begin{algorithmic}
      \Require{$\Enc$ is an IND-CCA \ac{PKE} scheme, $\Sign$ is a one-time 
        signature scheme.}
